{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-07-08 Notebook LaTEX/Momentum Accelerations/main.tex
>w< lots of updates to the notes

            \begin{definition}[Proximal Gradient Tri-Points Form E]
            \label{def:ag_tri_pt_form_E}
                Form E is a special case of 
                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$. 
                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$. 
                Giving us: 
                \begin{align*}
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \eta_t \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t).
                \end{align*}
            \end{definition}
            \begin{remark}

            \begin{definition}[Similar Triangle Form I]
            \label{def:ag_form_similar_tria_I}

@@

        \begin{theorem}[Generic AG Convergence]\label{thm:generic_smooth_ag_convergence}
            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
            \begin{align*}
                \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)
                \Upsilon_{2, t + 1}^{\text{AG}} + 
                \Upsilon_{1, t + 1}^{\text{AG}} \le 0, 
            \end{align*}
            then with 
            \begin{align*}
                \Phi_t &= \left(
                    \sum_{i = 1}^{t} \tilde\eta_{i}
                \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
                \\
                \Phi_0 &= \frac{1}{2}\Vert x_t - x_*\Vert^2, 
            \end{align*}
            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_T) - f(x_*)$. 
        \end{theorem}
        \begin{proof}
            By definition we have
            {\footnotesize
            \begin{align*}
                \Phi_{t + 1} - \Phi_t 
                &= 
                \left(
                    \sum_{i = 1}^{t+1} \tilde\eta_{i}
                \right) (f(z_{t + 1}) - f(x_*)) 
                - 
                \left(
                    \sum_{i = 1}^{t} \tilde\eta_{i}
                \right) (f(z_{t}) - f(x_*)) 
                + \frac{1}{2}\Vert x_t - x_*\Vert^2
                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
                \\
                &= 
                \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
                +
                \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)(f(z_{t + 1}) - f(z_t))
                + \frac{1}{2}\Vert x_t - x_*\Vert^2
                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
                \\
                &= \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le 0. 
            \end{align*}
            }
            The derivation for the convergence raet is direct and similar to 
            \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} 
            Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
        \end{proof}

    \subsection{Scenario I}
        In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
        \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}.
            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = 2/(2L)$, we derive the following algorithm: 
                x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t), 
                z_{t + 1} &= y_t - L^{-1} \nabla f(y_t), 
            Observe that this is the same algorithm as stated in Ryu's book but with an alternative choice of indexing for $y_t$ and initial condition. 
            Consider the upper bounds of $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$, together with the updates of the Generic Triangular Form of the algorithm:  
                x_{t + 1} - x_t &= \tilde \eta_{t + 1}\nabla f(y_t)
                z_{t +1} - y_t &= L^{-1}\nabla f(y_t), 
            we consider the upper bound of $\Upsilon_{1, t + 1}^{\text{AG}}$, with that we can simplify it: 
                -\frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
                \frac{\tilde \eta_{t + 1}L }{2} \Vert z_{t + 1} - y_t\Vert^2 
                \langle \tilde \eta_{t + 1} \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
                - \frac{1}{2}\Vert \tilde \eta_{t + 1} \nabla f(y_t)\Vert^2 
                + \frac{\tilde \eta_{t + 1} L}{2}\Vert L^{-1} \nabla f(y_t)\Vert^2 
                    - \tilde \eta_{t + 1} \nabla f(y_t), 
                    -L^{-1}\nabla f(y_t) + y_t - x_t + \tilde \eta_{t + 1}\nabla f(y_t)
                    \frac{\tilde \eta_{t + 1}^2}{2} + 
                    \frac{\tilde \eta_{t + 1}}{2L}
                \Vert \nabla f(y_t)\Vert^2 
                + \tilde \eta_{t + 1} 
                \left\langle 
                    \nabla f(y_t), 
                    (\tilde \eta_{t + 1} - L^{-1})\nabla f(y_t) + y_t - x_t 
                \right\rangle
                (1/2)(L^{-1}\tilde \eta_{t + 1} - \tilde \eta_{t + 1}^2)
                \Vert \nabla f(y_t)\Vert^2
                \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1})
                \Vert \nabla f(y_t)\Vert^2
                \tilde \eta_{t + 1}\langle \nabla f(y_t), y_t - x_t\rangle
                    -L^{-1}\tilde \eta_{t + 1} + \tilde \eta_{t + 1}^2
                \right)\Vert \nabla f(y_t)\Vert^2 
                \tilde\eta_{t + 1} \langle \nabla f(y_t), y_t - x_t\rangle. 
            For $\Upsilon_{2, t + 1}^\text{AG}$, we simplify it with the same updates relation in mind: 
                \langle \nabla f(y_t), z_{t +1} - y_t\rangle + 
                \frac{L}{2}\Vert z_{t +1} - y_{t} \Vert^2 
                    \nabla f(y_t), -L^{-1} \nabla f(y_t)
                \frac{L}{2}\Vert L^{-1}\nabla f(y_t) \Vert^ 2
                &= -\frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 
                + \langle \nabla f(y_t), y_t - z_t\rangle. 
            Hence let's consider $y_t - x_t = L \eta_t (z_t - y_t)$ from the algorithm, we make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \nabla f(y_t), y_t - x_t\rangle = \langle \nabla f(y_t), L \eta_t (z_t - y_t)\rangle$. 
            With this in mind, applying 
            \hyperref[thm:generic_smooth_ag_convergence]{theorem \ref*{thm:generic_smooth_ag_convergence}} 
            and upper bound from 
            \hyperref[lemma:smooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:smooth_agg_lyapunov_upper_bound}} 
            yields inequality: 
                & \Upsilon_{1, t + 1}^{\text{AG}} + \left(
                    \sum_{i=1}^{t}\tilde\eta_i 
                \right) \Upsilon_{2, t + 1}^{\text{AG}} 
                    -L^{-1}\tilde \eta_{t + 1} + \tilde \eta_{t + 1}^2
                \right)\Vert \nabla f(y_t)\Vert^2 
                \tilde\eta_{t + 1} \langle \nabla f(y_t), y_t - x_t\rangle
                    -\frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 
                    + \langle \nabla f(y_t), y_t - z_t\rangle
                \right)\Vert \nabla f(y_t)\Vert^2
                \tilde \eta_{t + 1}\langle \nabla f(y_t), L\eta_t (z_t - y_t)\rangle
                \langle \nabla f (y_t), y_t - z_t\rangle
                \right)\Vert \nabla f(y_t)\Vert^2
                \langle \nabla f(y_t), z_t - y_t\rangle. 
            Next, we select a choice for stepsize parameter $\eta_t, \tilde \eta_{t +1}$ such that the coefficient for the $\Vert \nabla f(y_t)\Vert^2$ is negative, and is zero for the cross product term. 
            In this scenario, we makes the choice of $\tilde \eta_t = \eta_t$. 
            Continuting will simplify the upper bound so that it is: 
                    \eta_{t + 1}^2 - L^{-1}\eta_{t +1} - L^{-1}\sum_{i = 1}^{t}\eta_i
                \right)\Vert \nabla f(y_t)\Vert^2
                \langle \nabla f(y_t), z_t - y_t\rangle 
            Assuming the above inequality holds then one of the sufficient conditions would happen when the coefficient of the cross product term is zero and the coefficient for the normed term is negative, yielding the condition for all $t \in \NN$: 
            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ is one of the options. 
            And there are not many other options for the choice of the stepszies for the equality to be satisfied. 
            In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify the algorithm in the literature. 

    \subsection{Scenario II}
        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
        The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario. 
        To start, we make the claim that the new stepsizes results in a different algorithm. 
        \begin{lemma}[Similar Triangular Form]
            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ as in \ref*{def:agg_tri}, we have the following specific similar triangular form of the accelerated gradient algorithm: 

@@

@@

            (\hyperref[thm:generic_smooth_ag_convergence]{theorem \ref*{thm:generic_smooth_ag_convergence}}) 

>>>>

            \begin{definition}[Proximal Gradient Tri-Points Form E]
            \label{def:ag_tri_pt_form_E}
                Form E is a special case of 
                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$. 
                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$. 
                Giving us: 
                \begin{align*}
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \eta_t \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t).
                \end{align*}
            \end{definition}

            \begin{definition}[Similar Triangle Form I]
            \label{def:ag_form_similar_tria_I}
                It updates iterates $(y_t, x_{t + 1}, z_{t + 1})$ using 
                \begin{align*}
                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t) 
                    \\
                    x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                    \\
                    y_{t + 1} &= 
                    (1 + L\eta_{t + 1})^{-1}
                    (
                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                    ). 
                \end{align*}
            \end{definition}
            \begin{observation}
                There are a lot of observations about this form to unpack. 
                Let's list the following observations
                \begin{enumerate}
                    \item Observe that $y_t = (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)$ is a convex combination between $x_t, z_t$. Hence $z_t, y_t, x_t$ are three collinear points. Additionally, we have $y_t - x_t = L\eta_t (z_t - y_t)$, hence $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$. 
                    \item By the algorithm, we have $z_{t + 1} - y_t = - L^{-1} \nabla f(y_t)$, and $x_{t + 1} - x_t = - \tilde \eta_{t + 1} \nabla f(y_t)$, hence vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$. 
                    \item Finally, with update $x_{t +1} - z_{t + 1} = L\eta_t (z_{t +1} - z_t)$, we have three colinear points $(z_t, z_{t + 1}, x_t)$ with $\Vert z_{t + 1} - z_t\Vert/\Vert z_{t +1 } - z_t\Vert = L\eta_t$. 
                \end{enumerate}
                From the above results, we can conclude that triangle $(y_t, z_t, z_{t + 1})$ is similar to $(x_t, z_t, x_{t + 1})$ because they share colinear points $z_t, y_t, x_t$ and $z_t, z_{t + 1}, x_{t + 1}$, and their sides $z_{t + 1} - y_t$ parallels to $x_{t + 1} - z_t$. 
            \end{observation}

@@

            \begin{lemma}[Similar Triangule Form I via Generic Tri Points]
                With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ 
                in 
                We can derive similar triangle form I as stated back in
                \hyperref[def:ag_form_similar_tria_I]{definition \ref*{def:ag_form_similar_tria_I}}. 

@@

        \begin{theorem}[Generic AG Convergence]
        \label{thm:generic_ag_convergence}
            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
            \begin{align*}
                \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)
                \Upsilon_{2, t + 1}^{\text{AG}} + 
                \Upsilon_{1, t + 1}^{\text{AG}} \le 0, 
            \end{align*}
            then with 
            \begin{align*}
                \Phi_t &= \left(
                    \sum_{i = 1}^{t} \tilde\eta_{i}
                \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
                \\
                \Phi_0 &= \frac{1}{2}\Vert x_t - x_*\Vert^2, 
            \end{align*}
            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_T) - f(x_*)$. 
        \end{theorem}
        \begin{proof}
            By definition we have
            {\footnotesize
            \begin{align*}
                \Phi_{t + 1} - \Phi_t 
                &= 
                \left(
                    \sum_{i = 1}^{t+1} \tilde\eta_{i}
                \right) (f(z_{t + 1}) - f(x_*)) 
                - 
                \left(
                    \sum_{i = 1}^{t} \tilde\eta_{i}
                \right) (f(z_{t}) - f(x_*)) 
                + \frac{1}{2}\Vert x_t - x_*\Vert^2
                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
                \\
                &= 
                \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
                +
                \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)(f(z_{t + 1}) - f(z_t))
                + \frac{1}{2}\Vert x_t - x_*\Vert^2
                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
                \\
                &= \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le 0. 
            \end{align*}
            }
            The derivation for the convergence raet is direct and similar to 
            \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} 
            Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
        \end{proof}

    \subsection{Scenario I}
        In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
        \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}. 
            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
            set $\eta_{t + 1} = \tilde \eta_{t + 1} = (t)/(2L)$, we derive the following algorithm: 
                x_{t + 1} &= x_t - \frac{t + 1}{2L} \mathcal G_L(y_t), 
                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t), 
            This algorithm has convergence rate of $\mathcal O(1/T^2)$ for all $h = f + g$ where $f$ is convex $L$-Lipschitz smooth and $g$ is convex. 
            Observe that when $g \equiv 0$ this is the same algorithm as 
            \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}
            but with an alternative choice of indexing for $y_t$ and initial condition. 
            Recall that for the proximal gradient PPM generic form we have iterate updates for $t\in \mathbb N$: 
                y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t). 
            and generic Lyapunov upper bound 
            By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations 
                x_{t + 1} - x_t &= -\tilde\eta_{t + 1}\mathcal G_L(y_t), 
                z_{t + 1} - y_t &= -L^{-1}\mathcal G_L(y_t). 
            This setup allows for: 
                \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2 
                \langle \tilde\eta_{t + 1}\mathcal G_L (y_t), x_{t + 1} - z_{t + 1} \rangle
                - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 
                \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), x_{t + 1} - z_{t + 1} \rangle
                    - \tilde\eta_{t + 1}^2 + 
                    L^{-1}\tilde\eta_{t + 1}
                \right)\Vert \mathcal G_L(y_t)\Vert^2
                    (x_{t + 1} - x_{t}) + x_t
                    + (y_t - z_{t + 1}) - y_t
                    L^{-1}\tilde\eta_{t + 1}
                    - \tilde\eta_{t + 1}^2
                \right)\Vert \mathcal G_L(y_t)\Vert^2
                    -\tilde\eta_{t + 1}\mathcal G_L(y_t) + x_t 
                    + L^{-1}\mathcal G_L(y_t) - y_t
                    L^{-1}\tilde\eta_{t + 1}
                    - \tilde\eta_{t + 1}^2
                \right)\Vert \mathcal G_L(y_t)\Vert^2
                    \tilde\eta_{t +1}\mathcal G_L(y_t), 
                    (L^{-1} - \tilde\eta_{t + 1})\mathcal G_L(y_t) + x_t - y_t
                    L^{-1}\tilde\eta_{t + 1} - \tilde\eta_{t + 1}^2 
                    + 2 \tilde\eta_{t + 1}^2 - 2\tilde\eta_{t + 1}L^{-1}
                \right)\Vert \mathcal G_L(y_t)\Vert^2
                    x_t - y_t
                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
                \right)\Vert \mathcal G_L(y_t)\Vert^2 
                + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle
            similarly we also have upper bound 
                \langle \mathcal G_L(y_t), z_{t + 1} - y_t + y_t - z_t\rangle
                \langle \mathcal G_L(y_t), - L^{-1} \mathcal G_L(y_t) + y_t - z_t\rangle
                \frac{L}{2}\Vert L^{-1}\mathcal G_L(y_t)\Vert^2
                -L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
                (1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
                \langle \mathcal G_L(y_t), y_t - z_t\rangle
                -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
                \langle \mathcal G_L(y_t), y_t - z_t\rangle
            Hence let's consider the update for $y_t$, which can be written as $y_t - x_t = L \eta_t (z_t - y_t)$. We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$. 
            With this in mind, applying the RHS of $[(*)]$ yields: 
                &\Upsilon_{1, t + 1}^\text{AG} + 
                    \sum_{i = 1}^{t}\tilde\eta_i 
                \right)\Upsilon_{1, t + 1}^{\text{AG}}
                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
                \right)\Vert \mathcal G_L(y_t)\Vert^2 
                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), L\eta_t(z_t - y_t)\rangle
                    \sum_{i = 1}^{t}\tilde\eta_i 
                    -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
                    \langle \mathcal G_L(y_t), y_t - z_t\rangle
                \right)\Vert \mathcal G_L(y_t)\Vert^2 + 
                \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle
            If the algorithm were to have the abstract convergence rate as stated in 
            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}},
            then one of the sufficient condition is to have the above quantity less than or equal to zero, one sufficient condition of that is to have the coefficient for $\Vert \mathcal G_L(y_t)\Vert$ be $\le 0$, and the coefficient of the cross term $\langle \mathcal G_L(y_t), z_t - y_t\rangle$ be zero. 
            To simplify, we make the assumption that $\tilde \eta_t = \eta_t$ for all $t \in \mathcal N$, making it to be a specific instance of 
            \hyperref[def:ag_tri_pt_form_E]{definition \ref*{def:ag_tri_pt_form_E}}. 
            These conditions translate to the following relations for $\eta_{t}$. 
            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ or $\eta_t = (t + 1)/2L$ are some of the options. 
            In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify this specific variant in the literature. 

    \subsection{Scenario II}
        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
        The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario. 
        % Recall similar a lemma about similar triangle form here.

@@

            (\hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}) 
